Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-25 paper.tex
update

%\item The randomness of the clumpy disk has an insignificant impact on the overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disk,\
%      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
%      indicating the dense disc is crucial for\
%      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).}
\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, possibly in balance with the IC and synchrotron cooling.\
      We will investigate the competition between stochastic acceleration and radiative cooling in a future work. {\color{red} KY: This item is to be modified according to the newly added text in the Discussion section.}
\end{itemize}

>>>>

%\item The randomness of the clumpy disk has an insignificant impact on the overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disk,\
%      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
%      indicating the dense disc is crucial for\
%      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures).}
\item The development of the expanding forward-reverse shock pair is always associated with the dense disk. Also, without the thin disk, only forward shocks exist. The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream. There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.

\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, possibly in balance with the IC and synchrotron cooling.\
      We will investigate the competition between stochastic acceleration and radiative cooling in a future work. {\color{red} KY: This item is to be modified according to the newly added text in the Discussion section.}
\end{itemize}
